Notes on Design and Implementation of Anglican

### 2015-07-17 paper/paper.tex
in progress

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{listings}

% For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}

@@

% Additional packages 
\usepackage{amsfonts}
%\usepackage{amsthm}
\usepackage{float}
\usepackage{enumitem}

@@

\begin{abstract}
\end{abstract}

@@

Anglican is implemented in just this way --- a macro facility
provided by Clojure, a Lisp dialect, is used both to add to
Clojure constructs that delimit probabilistic, rather than
deterministic, code, and to alter the operational semantics of
Clojure constructs inside probabilistic code fragments. Anglican
claims its right to count as a separate language because of the
ubiquitous probabilistic execution semantics rather than because
of a different syntax, which is actually an advantage rather
than a drawback --- Clojure programmers only need to know how to
specify the boundaries of Anglican programs, but can use
familiar Clojure syntax to write probabilistic code.

An implementation of Anglican must therefore address three issues:
\begin{itemize}
	\item the Clojure syntax to introduce probabilistic Anglican
		code inside Clojure modules;
	\item source-to-source transformation of Anglican programs
		into Clojure, so that probabilistic execution becomes
		possible;
	\item algorithms which run Clojure code, obtained by
		transforming Anglican programs, according to the
		probabilistic operational semantics.
\end{itemize}
The following sections explain the way Anglican is implemented,
from source-to-source transformation and syntactic wrappers to
inference algorithms which accept Clojure functions built from
anglican code as a parameter, and produce probabilistic outputs.

>>>>

\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}

\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{listings}

@@

@@

\begin{abstract}
	In these notes, are explain the rationale behind the
	macro-compiled implementation of Anglican, outline
	design choices, and describe important implementation
	aspects.
\end{abstract}

@@

Anglican is implemented in just this way --- a macro facility
provided by Clojure, a Lisp dialect, is used both to add to
Clojure constructs that delimit probabilistic, rather than
deterministic, code, and to alter the operational semantics of
Clojure expressions inside probabilistic code fragments. Anglican
claims its right to count as a separate language because of the
ubiquitous probabilistic execution semantics rather than because
of a different syntax, which is actually an advantage rather
than a drawback --- Clojure programmers only need to know how to
specify the boundaries of Anglican programs, but can use
familiar Clojure syntax to write probabilistic code.

An implementation of Anglican must therefore address three issues:
\begin{itemize}
	\item the Clojure syntax to introduce probabilistic Anglican
		code inside Clojure modules;
	\item source-to-source transformation of Anglican programs
		into Clojure, so that probabilistic execution becomes
		possible;
	\item algorithms which run Clojure code, obtained by
		transforming Anglican programs, according to the
		probabilistic operational semantics.
\end{itemize}
The following sections explain the way Anglican is implemented,
from source-to-source transformation and syntactic wrappers to
inference algorithms which accept Clojure functions built from
Anglican code as a parameter, and produce probabilistic outputs.
